---
title: "UnicornCompaniesFeatureAnalysis"
output: html_document
date: '2022-05-06'
---

```{r setup, include=FALSE}
library(tidyverse)

```

## R Markdown


```{r cars}
unicorn_data=read.csv("../Unicorn_Companies_cleaned.csv")

names(unicorn_data)
```

Yearly graph

```{r}



```



```{r}
country_group=unicorn_data%>%group_by(Country)%>%summarise(Number_companies_per_country=n())%>%arrange(desc(Number_companies_per_country))
country_group

# ggplot(data = country_group, aes(x = Country, y = Number_companies_per_country)) +
# geom_point(aes(fill = Country))+ ggtitle("Country vr Decor") + xlab("Country")+ ylab("Number Companies") 


ggplot(country_group[1:10,], aes(x = reorder(Country,desc(Number_companies_per_country)), y = Number_companies_per_country)) +
  geom_col(fill = "#401ABE") +
  labs(
    x = "Country",
    y = "Number unicorns"
  ) +
  theme(
    axis.title.x = element_text(size = 15),
    axis.title.y = element_text(size = 15),
    #axis.text = element_text(angle = 10, hjust = 1)
    
  )+geom_text(aes(label=Number_companies_per_country), position=position_dodge(width=0.9), vjust=-0.25)

###count percentage
total=sum(country_group$Number_companies_per_country)
country_group$Percentage=country_group$Number_companies_per_country*100/total
country_group

top4_other=country_group[1:4,]
top4_sum=sum(top4_other$Number_companies_per_country)
top4_sum
top4_other
top4_other=rbind(top4_other, data.frame(Country='Others', Number_companies_per_country=total-top4_sum, Percentage=(total-top4_sum)*100/total))

ggplot(top4_other, aes(x = reorder(Country,desc(Percentage)), y = Number_companies_per_country)) +
  geom_col(fill = "#401ABE") +
  labs(
    x = "Country",
    y = "Number Companies"
  ) +
  theme(
    axis.title.x = element_text(color = "#401ABE", size = 15, face = "bold"),
    axis.title.y = element_text(size = 15, face = "italic"),
    #axis.text = element_text(angle = 10, hjust = 1)
    
  )+geom_text(aes(label=round(Percentage)), position=position_dodge(width=0.9), vjust=-0.25)

ggplot(top4_other, aes(x="", y=Percentage, fill=Country)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)


```

## Including Plots
##Cleaning Data her


```{r}
#install.packages("stringi")
library(stringi)
library(lubridate)

str(unicorn_data)

unique(unicorn_data$Industry)

unicorn_data_updated=unicorn_data


names(unicorn_data_updated)[names(unicorn_data_updated) == "Valuation...B."] <- "Valuation_in_B"  

names(unicorn_data_updated)
  

unicorn_data_updated$Valuation_in_B <- gsub('$', '', unicorn_data_updated$Valuation_in_B, fixed = T)
unicorn_data_updated

unicorn_data_updated$Valuation_in_B <- as.numeric(unicorn_data_updated$Valuation_in_B)

unicorn_data_updated$Date.Joined <- as.Date(unicorn_data_updated$Date.Joined , format = "%m/%d/%Y")


unicorn_data_updated$Total.Raised <- gsub('$', '', unicorn_data_updated$Total.Raised, fixed = T)
stri_sub(unicorn_data_updated$Total.Raised[1],-1)
?stri_sub



unicorn_data_updated=unicorn_data_updated%>%mutate(Total_Raised_num=stri_sub(unicorn_data_updated$Total.Raised, from=1, to=stri_length(unicorn_data_updated$Total.Raised)-1))

#unicorn_data_updated = subset(unicorn_data_updated, select = -c(Total_Raised_unit) )

unicorn_data_updated=unicorn_data_updated%>%mutate(Total_Raised_unit=stri_sub(unicorn_data_updated$Total.Raised,-1))
unicorn_data_updated



unicorn_data_updated$Total_Raised_num <- as.numeric(unicorn_data_updated$Total_Raised_num)
unicorn_data_updated

unicorn_data_updated

unicorn_data_updated=unicorn_data_updated%>%mutate(Total_Raised_num=ifelse(Total_Raised_unit=='M',(Total_Raised_num/1000),Total_Raised_num) )

unicorn_data_updated


names(unicorn_data_updated)[names(unicorn_data_updated) == "Total_Raised_num"] <- "Total_Raised_in_B"
unicorn_data_updated$Founded.Year=as.numeric(unicorn_data_updated$Founded.Year)
str(unicorn_data_updated)



unicorn_data_updated=unicorn_data_updated%>%mutate(number_of_years=year(unicorn_data_updated$Date.Joined)-unicorn_data_updated$Founded.Year )
```
Yearly:
```{r}
library(lubridate)
a=mdy(b)
year(a)
year(mdy((unicorn_data$Date.Joined)))

year_group=unicorn_data_updated%>%group_by(Year=year(mdy((unicorn_data$Date.Joined))))%>%summarise(Number_of_companies_yearly=n())


ggplot(year_group, aes(x = reorder(Year,(Year)), y = Number_of_companies_yearly)) +
  geom_col(fill = "#401ABE") +
  labs(
    x = "Year",
    y = "Number of new unicorns per year"
  ) +
  theme(
    axis.title.x = element_text(size = 17),
    axis.title.y = element_text(size = 17),
    axis.text = element_text(size = 10)
    
  )+geom_text(aes(label=round(Number_of_companies_yearly)), position=position_dodge(width=0.9), vjust=-0.25)



```




```{r}
#Heat Map

# install.packages("ggplot2")
#library(ggplot2)

ggplot(unicorn_data_updated, aes(x = names(unicorn_data_updated), y = names(unicorn_data_updated), fill = cor(x,y))) +
  geom_tile(color = "black") +
  geom_text(aes(label = value), color = "white", size = 4) +
  coord_fixed() 

?cor()
str(unicorn_data_updated)
```


```{r}
vec=c(unicorn_data_updated$Valuation_in_B,unicorn_data_updated$number_of_years,unicorn_data_updated$Total_Raised_in_B)
cor(vec,vec, use = "complete.obs")
crltn

cor(unicorn_data_updated$Valuation_in_B,unicorn_data_updated$number_of_years, use = "complete.obs")

cor(unicorn_data_updated$Valuation_in_B,unicorn_data_updated$Total_Raised_in_B, use = "complete.obs")

str(unicorn_data_updated)
unicorn_data_updated$Investors.Count=as.numeric(unicorn_data_updated$Investors.Count)

```

#linear model
```{r}
model = lm(Valuation_in_B ~ Investors.Count , data = unicorn_data_updated) #Use the linear model function lm() to
                                  #conduct the simple linear regression.
summary(model)
plot(model)

plt=ggplot(data = unicorn_data_updated, aes(x = Investors.Count, y =Valuation_in_B ))+ geom_point()+ ggtitle("Number of Investors versus Valuation in Billion") + xlab("Number of investors")+ ylab("Valuation in billion $")+
  theme(
    axis.title.x = element_text(size = 17),
    axis.title.y = element_text(size = 17),
    axis.text = element_text(size = 10)
    
  )
plt_con_line=plt+geom_smooth(method = lm) #confidence interval
plt_con_line





###########After removing top 0.5 percent
AftertopXper<-function(x){
  
  top0.5per=x*length(unicorn_data_updated$Valuation_in_B)/100
  thrshld_val=unicorn_data_updated$Valuation_in_B[top0.5per]
  
  unicorn_data_updated_99.5Valuation=unicorn_data_updated
  unicorn_data_updated_99.5Valuation=unicorn_data_updated_99.5Valuation%>%filter(Valuation_in_B<thrshld_val)
  
  model1 = lm(Valuation_in_B ~ Investors.Count , data = unicorn_data_updated_99.5Valuation) #Use the linear model function lm() to
                                  #conduct the simple linear regression.
  print(summary(model1))
  plot(model1)
  
  plt1=ggplot(data = unicorn_data_updated_99.5Valuation, aes(x = Investors.Count, y =Valuation_in_B ))+ geom_point()+ ggtitle("Number of Investors versus Valuation in Billion") + xlab("Number of Investors")+ ylab("Valuation in Billion")
  plt_con_line1=plt1+geom_smooth(method = lm) #confidence interval
    plt_con_line1
    
  }
  
  
  AftertopXper(0.5)

  AftertopXper(1)

```

#linear regression for USA

```{r}
unicorn_data_US=unicorn_data_updated%>%filter(Country=="United States")
unicorn_data_US

model_us = lm(Valuation_in_B ~ Investors.Count , data = unicorn_data_US) #Use the linear model function lm() to
                                  #conduct the simple linear regression.
summary(model_us)
plot(model_us)

plt=ggplot(data = unicorn_data_US, aes(x = Investors.Count, y =Valuation_in_B ))+ geom_point()+ ggtitle("Number of Investors versus Valuation in Billion") + xlab("Investors.Count")+ ylab("Valuation in Billion")
plt_con_line=plt+geom_smooth(method = lm) #confidence interval
plt_con_line





###########After removing top 0.5 percent
AftertopXper<-function(x){

  top0.5per=x*length(unicorn_data_US$Valuation_in_B)/100
  thrshld_val=unicorn_data_US$Valuation_in_B[top0.5per]

  unicorn_data_updated_99.5Valuation=unicorn_data_US
  unicorn_data_updated_99.5Valuation=unicorn_data_updated_99.5Valuation%>%filter(Valuation_in_B<thrshld_val)

  model1 = lm(Valuation_in_B ~ Investors.Count , data = unicorn_data_updated_99.5Valuation) #Use the linear model function lm() to
                                  #conduct the simple linear regression.
  print(summary(model1))
  plot(model1)

  plt1=ggplot(data = unicorn_data_updated_99.5Valuation, aes(x = Investors.Count, y =Valuation_in_B ))+ geom_point()+ ggtitle("Number of Investors versus Valuation in Billion") + xlab("Investors.Count")+ ylab("Valuation in Billion")
  plt_con_line1=plt1+geom_smooth(method = lm) #confidence interval
    plt_con_line1

  }


  #AftertopXper(0.5)

  AftertopXper(1)

```
#Linear Regression China

```{r}

unicorn_data_china=unicorn_data_updated%>%filter(Country=="China")
unicorn_data_china

model_us = lm(Valuation_in_B ~ Investors.Count , data = unicorn_data_china) #Use the linear model function lm() to
                                  #conduct the simple linear regression.
summary(model_us)
plot(model_us)

plt=ggplot(data = unicorn_data_china, aes(x = Investors.Count, y =Valuation_in_B ))+ geom_point()+ ggtitle("Number of Investors versus Valuation in Billion") + xlab("Investors.Count")+ ylab("Valuation in Billion")
plt_con_line=plt+geom_smooth(method = lm) #confidence interval
plt_con_line





###########After removing top 0.5 percent
AftertopXper<-function(x){

  top0.5per=x*length(unicorn_data_china$Valuation_in_B)/100
  thrshld_val=unicorn_data_china$Valuation_in_B[top0.5per]

  unicorn_data_updated_99.5Valuation=unicorn_data_china
  unicorn_data_updated_99.5Valuation=unicorn_data_updated_99.5Valuation%>%filter(Valuation_in_B<thrshld_val)

  model1 = lm(Valuation_in_B ~ Investors.Count , data = unicorn_data_updated_99.5Valuation) #Use the linear model function lm() to
                                  #conduct the simple linear regression.
  print(summary(model1))
  plot(model1)

  plt1=ggplot(data = unicorn_data_updated_99.5Valuation, aes(x = Investors.Count, y =Valuation_in_B ))+ geom_point()+ ggtitle("Number of Investors versus Valuation in Billion") + xlab("Investors.Count")+ ylab("Valuation in Billion")
  plt_con_line1=plt1+geom_smooth(method = lm) #confidence interval
    plt_con_line1

  }


  #AftertopXper(0.5)

  AftertopXper(1)

```````


```{r}
#valuation vrs (Investors and years since formed)
library(car)
as.numeric(format(Sys.Date(), "%Y"))-unicorn_data_updated$Founded.Year

unicorn_data_updated=unicorn_data_updated%>%mutate(Years_since_founded=as.numeric(format(Sys.Date(), "%Y"))-unicorn_data_updated$Founded.Year)
unicorn_data_updated

model_invstr_yr <- lm(Valuation_in_B~+Investors.Count+Years_since_founded, data = unicorn_data_updated)

# Show the model.
print(summary(model_invstr_yr))

plot(model_invstr_yr)
vif(model_invstr_yr)
#avPlot(model_invstr_yr)

plt2=ggplot(data = unicorn_data_updated, aes(x = Investors.Count, y =Valuation_in_B ))+ geom_point()+ ggtitle("Number of Investors versus Valuation in Billion") + xlab("Investors.Count")+ ylab("Valuation in Billion")
plt_con_line2=plt2+geom_smooth(method = lm) #confidence interval
plt_con_line2

```
USA multi

```{r}

# as.numeric(format(Sys.Date(), "%Y"))-unicorn_data_updated$Founded.Year
# 
# unicorn_data_updated=unicorn_data_updated%>%mutate(Years_since_founded=as.numeric(format(Sys.Date(), "%Y"))-unicorn_data_updated$Founded.Year)
# unicorn_data_updated
# 


data_us=unicorn_data_updated%>%filter(Country=="United States")


model_invstr_yr_us <- lm(Valuation_in_B~+Investors.Count+Years_since_founded, data = data_us)

# Show the model.
print(summary(model_invstr_yr_us))

plot(model_invstr_yr_us)
vif(model_invstr_yr_us)
#avPlot(model_invstr_yr)

plt2=ggplot(data = unicorn_data_updated, aes(x = Investors.Count, y =Valuation_in_B ))+ geom_point()+ ggtitle("Number of Investors versus Valuation in Billion") + xlab("Investors.Count")+ ylab("Valuation in Billion")
plt_con_line2=plt2+geom_smooth(method = lm) #confidence interval
plt_con_line2


```

China:

```{r}
data_china=unicorn_data_updated%>%filter(Country=="China")


model_invstr_yr_china <- lm(Valuation_in_B~+Investors.Count+Years_since_founded, data = data_china)

# Show the model.
print(summary(model_invstr_yr_china))

plot(model_invstr_yr_china)
vif(model_invstr_yr_china)

```







```{r}

unique(unicorn_data_updated$Industry)
unicorn_data_updated$Industry <- gsub('Finttech', 'Fintech', unicorn_data_updated$Industry)

unicorn_data_updated$Industry <- gsub('Artificial intelligence', 'Artificial Intelligence', unicorn_data_updated$Industry)




sum(is.na(unicorn_data_updated$Industry))
sum(is.na(unicorn_data_updated$number_of_years))
industry_year_tmp=unicorn_data_updated%>%select(Industry,number_of_years)
unique(industry_year_tmp$Industry)

industry_year_tmp=industry_year_tmp %>% drop_na()
sum(is.na(industry_year_tmp$number_of_years))
sum(unicorn_data_updated$Select.Inverstors=="None")

industry_year_group=industry_year_tmp%>%group_by(Industry)%>%summarise(Avg_years=mean(number_of_years))
industry_year_group

ggplot(industry_year_group, aes(x = reorder(Industry,(Avg_years)), y = Avg_years)) +
  geom_col(fill = "#401ABE") +
  labs(
    x = "Industry",
    y = "Average years to become unicorn"
  ) +
  theme(
    axis.title.x = element_text(size = 18),
    axis.title.y = element_text(size = 18),
    axis.text = element_text(size=10.0 ,angle = 45, hjust = 1)
    
  )+geom_text(aes(label=round(Avg_years)), position=position_dodge(width=1), vjust=-0.3)





```
```{r}
#Countrywise
countrywise<-function(cnrty){
  unicorn_data_updated_tmp=unicorn_data_updated%>%filter(Country==cnrty)

sum(is.na(unicorn_data_updated_tmp$Industry))
sum(is.na(unicorn_data_updated_tmp$number_of_years))
industry_year_tmp=unicorn_data_updated_tmp%>%select(Industry,number_of_years)
unique(industry_year_tmp$Industry)

industry_year_tmp=industry_year_tmp %>% drop_na()
sum(is.na(industry_year_tmp$number_of_years))
sum(unicorn_data_updated_tmp$Select.Inverstors=="None")

industry_year_group=industry_year_tmp%>%group_by(Industry)%>%summarise(Avg_years=mean(number_of_years),Total_companies=n())
print(industry_year_group)

ggplot(industry_year_group, aes(x = reorder(Industry,desc(Avg_years)), y = Avg_years)) +
  geom_col(fill = "#401ABE") +
  labs(
    x = "Industry",
    y = "Avg years" #,
    #title=cnrty
  ) +
  theme(
    axis.title.x = element_text( size = 15, face = "bold"),
    axis.title.y = element_text(size = 15, face = "italic"),
    axis.text = element_text(angle = 45, hjust = 1)
    
  )+geom_text(aes(label=round(Avg_years)), position=position_dodge(width=1), vjust=-0.3)
}

unique(unicorn_data_updated$Industry)


US_df=countrywise("United States")
China_df=countrywise("China")
India_df=countrywise("India")





#which secot is most in which country

# ggplot(industry_year_group, aes(x = reorder(Industry,desc(Total_companies)), y = Avg_years)) +
#   geom_col(fill = "#401ABE") +
#   labs(
#     x = "Industry",
#     y = "Avg years" #,
#     #title=cnrty
#   ) +
#   theme(
#     axis.title.x = element_text( size = 15, face = "bold"),
#     axis.title.y = element_text(size = 15, face = "italic"),
#     axis.text = element_text(angle = 45, hjust = 1)
#     
#   )+geom_text(aes(label=round(Avg_years)), position=position_dodge(width=1), vjust=-0.3)



```
Investor's Analysis

```{r}



```




Matrix creation:

```{r}
lstt=split(unicorn_data_updated$Select.Inverstors[1],",")
lstt=unlist(lstt, recursive = TRUE, use.names = TRUE)

length(lstt)


Names <- unicorn_data_updated$Select.Inverstors[1]

length(unicorn_data_updated$Select.Inverstors)

lstt=strsplit(unicorn_data_updated$Select.Inverstors[1], split = ",")
lstt[1]

num_invstr_lst=c()
for (i in 1:length(unicorn_data_updated$Select.Inverstors)) {
  num_invstr_lst[i]=(length(unlist(strsplit(unicorn_data_updated$Select.Inverstors[i], split = ","), recursive = TRUE, use.names = TRUE)))
}


max(num_invstr_lst)
```


```{r}
investors_seperated=separate(unicorn_data_updated, col=Select.Inverstors, into=c('Investor1', 'Investor2', 'Investor3', 'Investor4'), sep=',')

inv1=c()

inv1=unique(investors_seperated$Investor1)
inv2=unique(investors_seperated$Investor2)
inv3=unique(investors_seperated$Investor3)
inv4=unique(investors_seperated$Investor4)

str(inv1)

invstr_set1=union(inv1,inv2)
invstr_set2=union(inv3,inv4)

all_unique_investors=(union(invstr_set1,invstr_set2))

col_vec=c('Index',all_unique_investors)
col_vec
df <- data.frame(matrix(ncol = length(all_unique_investors)+1, nrow = length(all_unique_investors)))
colnames(df) <- col_vec

df

df$Index <- all_unique_investors

#names(df)%>%grep(" ","_")


names(df)<-gsub(' ', '_', names(df))

df$Index<-gsub(' ', '_', df$Index)

df

dF$Weight[which(DF$Fruits == "Sequoia_Capital_China")] <- NA



investors_seperated

```


Each Investor invested in how many comparies

```{r}

investors_seperated

group1=investors_seperated%>%group_by(Investor1)%>%summarise(num_companies=n())
group2=investors_seperated%>%group_by(Investor2)%>%summarise(num_companies=n())
group3=investors_seperated%>%group_by(Investor3)%>%summarise(num_companies=n())
group4=investors_seperated%>%group_by(Investor4)%>%summarise(num_companies=n())

group3$Investor3<-gsub('\t', '', group3$Investor3)
group4$Investor4<-gsub('\t', '', group4$Investor4)

names(group2)[names(group2) == "Investor2"] <- "Investor1"
group2$Investor1<-gsub('\t', '', group2$Investor1)

group2
new_group=rbind(group1,group2)
new_group
group1
group2

new_group$Investor1 <- trimws(new_group$Investor1, which = c("left"))
new_group

new_group1=new_group%>% group_by(Investor1) %>% summarise(num_companies = sum(num_companies))

new_group1


names(group3)[names(group3) == "Investor3"] <- "Investor1"

new_group2=rbind(new_group1,group3)
new_group2
new_group2$Investor1 <- trimws(new_group2$Investor1, which = c("left"))

new_group3=new_group2%>%group_by(Investor1)%>%summarise(num_companies=sum(num_companies))
new_group3



names(group4)[names(group4) == "Investor4"] <- "Investor1"
new_group3
new_group4=rbind(new_group3,group4)
new_group4
new_group4$Investor1 <- trimws(new_group4$Investor1, which = c("left"))
new_group5=new_group4%>%group_by(Investor1)%>%summarise(num_companies=sum(num_companies))
new_group5


final_df_all_investors_number_of_investments=new_group5
final_df_all_investors_number_of_investments
final_df_all_investors_number_of_investments1=final_df_all_investors_number_of_investments %>% drop_na()
final_df_all_investors_number_of_investments1=final_df_all_investors_number_of_investments1[order(desc(final_df_all_investors_number_of_investments1$num_companies)),]
nrow(final_df_all_investors_number_of_investments1)
final_df_all_investors_number_of_investments1
  
final_df_all_investors_number_of_investments1=final_df_all_investors_number_of_investments1%>%filter(Investor1!="") 
final_df_all_investors_number_of_investments

final_df_all_investors_number_of_investments1=final_df_all_investors_number_of_investments1%>%filter(Investor1!="/td>") 

final_df_all_investors_number_of_investments1

final_df_all_investors_number_of_investments1$index <- 1:nrow(final_df_all_investors_number_of_investments1)
final_df_all_investors_number_of_investments1

ggplot(final_df_all_investors_number_of_investments1, aes(x=index, y=num_companies)) + geom_point()
# Change the point size, and shape
# ggplot(mtcars, aes(x=wt, y=mpg)) +
#   geom_point(size=2, shape=23)



```
Investors Vrs Number of companies invested
```{r}

final_df_all_investors_number_of_investments1%>%filter(num_companies==1)


ggplot(final_df_all_investors_number_of_investments1[1:20,], aes(x="Investor1", y=num_companies)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)

ggplot(final_df_all_investors_number_of_investments1[1:20,], aes(x = reorder(Investor1,desc(num_companies)), y = num_companies)) +
  geom_col(fill = "#401ABE") +
  labs(
    x = "Investors",
    y = "Number of companies"
  ) +
  theme(
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    axis.text = element_text(size = 13,angle = 45, hjust = 1)
    
  )+geom_text(aes(label=round(num_companies)), position=position_dodge(width=0.9), vjust=-0.25)


```



#Investor grouping


```{r}
#getAllPairFromUnicorn<-function(x){
# A=c(Sequoia Capital China, SIG Asia Investments, Sina Weibo, Softbank Group)
# B=c('a','b','c','d')
# xx=c("Sequoia Capital China", "SIG Asia Investments", "Sina Weibo", "Softbank Group")
# #xx<-gsub(" ","_",xx)
# unicorn_data_updated$Select.Inverstors[1]
# 
# xx=unicorn_data_updated$Select.Inverstors[1]

getAllPairFromUnicorn<-function(xx){
  #print(xx)
  xx<-gsub(", ",",",xx)
  #print(xx)
  lstt=strsplit(xx, split = ",")
  #lstt[1]
  lstt=unlist(lstt, recursive = TRUE, use.names = TRUE)
  length(lstt)
  
  lstt=sort(lstt)
  
  a=(combn(lstt, 2))
  df=as.data.frame(a)
  rslt=paste(df[1,],df[2,], sep = ",")
  return(rslt)
}

getAllPairFromUnicorn(unicorn_data_updated$Select.Inverstors[3])

for(i in 1:length(investors_col)){
  print(investors_col[i])
  if(grepl(',',investors_col[i])==TRUE){
    getAllPairFromUnicorn      
  }
  
  
}



###############################

tuple_investors <- data.frame(Tuple=character(),
                 Tuple_count=integer())


names(tuple_investors)


for(i in 1:length(investors_col)){
  #print(investors_col[i])
  if(grepl(',',investors_col[i])==TRUE){
    print(getAllPairFromUnicorn(investors_col[i]))
    
    
    
    ##########################################################
    tpl_set=getAllPairFromUnicorn(investors_col[i])
    sz=length(tpl_set)
    for(j in 1:sz){
      print(tpl_set[j])
      
      if(tpl_set[j] %in% tuple_investors$Tuple){
        val=as.numeric(tuple_investors[tuple_investors$Tuple==tpl_set[j], "Tuple_count"])
        tuple_investors[tuple_investors$Tuple==tpl_set[j], "Tuple_count"]<-val+1
        
      }else{
        tuple_investors[nrow(tuple_investors) + 1,] <- c(tpl_set[j],1)
      }
      
    }
    
    ##########################################################
    
  }
  
  
}

tuple_investors2=tuple_investors

tuple_investors2=tuple_investors2[order(desc(tuple_investors2$Tuple_count)),]
nrow(tuple_investors2)
tuple_investors2


tuple_investors2$index <- 1:nrow(tuple_investors2)
tuple_investors2

ggplot(tuple_investors2, aes(x=index, y=Tuple_count)) + geom_point()+
  labs(
    x = "Pairs (2-tuple) investors sorted by number of unicorns they've invested in",
    y = "Number of unicorns"
  ) +
  theme(
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    #axis.text = element_text(size = 13,angle = 45, hjust = 1)
    
  )



# df_test <- data.frame(Tuple=character(),
#                  Tuple_count=integer())
# df_test$Tuple
# 
# tpl_set=getAllPairFromUnicorn(investors_col[1])
# sz=length(tpl_set)
# for(i in 1:sz){
#   print(tpl_set[i])
#   
#   if(tpl_set[i] %in% df_test$Tuple){
#     val=as.numeric(df_test[df_test$Tuple==tpl_set[i], "Tuple_count"])
#     df_test[df_test$Tuple==tpl_set[i], "Tuple_count"]<-val+1
#     
#   }else{
#     df_test[nrow(df_test) + 1,] <- c(tpl_set[i],1)
#   }
#   
# }
# 
# 
# 
# 
# 
# df_test







```




Tuple analysis (cleaned code)
```{r}

getAllPairFromUnicorn<-function(xx){
  xx<-gsub(", ",",",xx)
  lstt=strsplit(xx, split = ",")
  lstt=unlist(lstt, recursive = TRUE, use.names = TRUE)
  length(lstt)
  lstt=sort(lstt)
  a=(combn(lstt, 2))
  df=as.data.frame(a)
  rslt=paste(df[1,],df[2,], sep = ",")
  return(rslt)
}

getAllTripletFromUnicorn<-function(xx){
  xx<-gsub(", ",",",xx)
  lstt=strsplit(xx, split = ",")
  lstt=unlist(lstt, recursive = TRUE, use.names = TRUE)
  length(lstt)
  lstt=sort(lstt)
  print(lstt)
  a=(combn(lstt, 3))
  df=as.data.frame(a)
  rslt=paste(df[1,],df[2,],df[3,], sep = ",")
  return(rslt)
}

getAllFourFromUnicorn<-function(xx){
  xx<-gsub(", ",",",xx)
  lstt=strsplit(xx, split = ",")
  lstt=unlist(lstt, recursive = TRUE, use.names = TRUE)
  length(lstt)
  lstt=sort(lstt)
  print(lstt)
  a=(combn(lstt, 4))
  df=as.data.frame(a)
  rslt=paste(df[1,],df[2,],df[3,],df[4,], sep = ",")
  return(rslt)
}



print(unicorn_data_updated$Select.Inverstors[1])

print(getAllTripletFromUnicorn(unicorn_data_updated$Select.Inverstors[1]))



tupleCountFunc<-function(investors_col,tple_size){
  
  tuple_investors <- data.frame(Tuple=character(),
                 Tuple_count=integer())


for(i in 1:length(investors_col)){
  
  comm_cont=str_count(unicorn_data_updated$Select.Inverstors[i], ',')
  
  #if(grepl(',',investors_col[i])==TRUE){
  if(comm_cont>=(tple_size-1)){
    print(comm_cont)
    print(tple_size-1)
    
    if(tple_size==2){
      tpl_set=getAllPairFromUnicorn(investors_col[i])
    }else if(tple_size==3){
      tpl_set=getAllTripletFromUnicorn(investors_col[i])
    }else if(tple_size==4){
       tpl_set=getAllFourFromUnicorn(investors_col[i])
    }else{
       tpl_set=getAllPairFromUnicorn(investors_col[i])
    }
    
    sz=length(tpl_set)
    for(j in 1:sz){
      if(tpl_set[j] %in% tuple_investors$Tuple){
        val=as.numeric(tuple_investors[tuple_investors$Tuple==tpl_set[j], "Tuple_count"])
        tuple_investors[tuple_investors$Tuple==tpl_set[j], "Tuple_count"]<-val+1
        
      }else{
        tuple_investors[nrow(tuple_investors) + 1,] <- c(tpl_set[j],1)
      }
      
    }
    
  }
  
  
}
  return(tuple_investors)
  
}

########two tuple################

tuple_investors2=tupleCountFunc(unicorn_data_updated$Select.Inverstors,2)

tuple_investors2=tuple_investors2[order(desc(tuple_investors2$Tuple_count)),]
nrow(tuple_investors2)
tuple_investors2


tuple_investors2$index <- 1:nrow(tuple_investors2)
tuple_investors2

ggplot(tuple_investors2, aes(x=index, y=Tuple_count)) + geom_point()

#########three tuple###############
tuple_investors3=tupleCountFunc(unicorn_data_updated$Select.Inverstors,3)
tuple_investors3

tuple_investors3=tuple_investors3[order(desc(tuple_investors3$Tuple_count)),]
nrow(tuple_investors3)
tuple_investors3

#########Four tuple###############
tuple_investors4=tupleCountFunc(unicorn_data_updated$Select.Inverstors,4)
tuple_investors4

tuple_investors4=tuple_investors4[order(desc(tuple_investors4$Tuple_count)),]
nrow(tuple_investors4)
tuple_investors4

```


```{r}
tuple_investors2

#tuple_investors2 %>% separate(Tuple, c('Investor1', 'Investor2'))
tuple_investors2[c('Investor1', 'Investor2')] <- str_split_fixed(tuple_investors2$Tuple, ',', 2)
investor_input <- readline(prompt="Enter investor name: ")
tuple_investors2%>%filter(Investor1==investor_input)

accel_partners=tuple_investors2%>%filter(Investor1=="Accel")
accel_partners_top=accel_partners%>%filter(Tuple_count>=2)

ggplot(accel_partners_top, aes(x = reorder(Investor2,desc(Tuple_count)), y = Tuple_count)) +
  geom_col(fill = "#401ABE") +
  labs(
    x = "Investors",
    y = "Number of investments with Accel"
  ) +
  theme(
    axis.title.x = element_text(size = 15, face = "bold"),
    axis.title.y = element_text(size = 15, face = "bold"),
    axis.text = element_text(angle = 45, hjust = 1)
    
  )+geom_text(aes(label=Tuple_count), position=position_dodge(width=0.9), vjust=-0.25)




#################### Tiger Global Management

tiger_partners=tuple_investors2%>%filter(Investor1=="Tiger Global Management")
tiger_partners_top=accel_partners%>%filter(Tuple_count>=2)

ggplot(tiger_partners_top, aes(x = reorder(Investor2,desc(Tuple_count)), y = Tuple_count)) +
  geom_col(fill = "#401ABE") +
  labs(
    x = "Investors",
    y = "Number Companies Invested Together"
  ) +
  theme(
    axis.title.x = element_text(color = "#401ABE", size = 15, face = "bold"),
    axis.title.y = element_text(size = 15, face = "italic"),
    axis.text = element_text(angle = 45, hjust = 1)
    
  )+geom_text(aes(label=Tuple_count), position=position_dodge(width=0.9), vjust=-0.25)




```


Valuation:

```{r}

unicorn_data_updated_tmmpp=unicorn_data_updated


unicorn_data_updated_tmmpp=unicorn_data_updated_tmmpp[order(desc(unicorn_data_updated_tmmpp$Valuation_in_B)),]
nrow(tuple_investors2)
tuple_investors2


unicorn_data_updated_tmmpp$index <- 1:nrow(unicorn_data_updated_tmmpp)
unicorn_data_updated_tmmpp

ggplot(unicorn_data_updated_tmmpp, aes(x=index, y=Valuation_in_B)) + geom_point()+
  labs(
    x = "Companies sorted by their valuation Rank",
    y = "Valuation in billion $"
  ) +
  theme(
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    #axis.text = element_text(size = 13,angle = 45, hjust = 1)
    
  )

```


